Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-03 WSSSPE1_report/WSSSPE1_summary_report.tex
adding a note, fixing some spelling

@@

WSSSPE1 was organized in collaboration of the relatively small group of organizers and
a larger peer-review commitee. This commitee had early influence on the organization,
e.g., on the specific call for papers.

>>>>

\todo{mention arXiv:1311.3523 and explain what's different here}

@@

WSSSPE1 was organized in collaboration of the relatively small group of organizers and
a larger peer-review committee. This committee had early influence on the organization,
e.g., on the specific call for papers.
